---
title: "Alcohol vs Seat choice"
author: "Saul Perez Ramos"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The people in the back seat have a higher consumption of alcohol compared to the people in the middle and the front seat. The median for the people that are in the back is higher than the top 75 percentile of the front seat and the middle seat people. 

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```
The mean for the back seat people is three times as much than the people in the middle seats and even more than the people in the front seats.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
since the p value from one way anova was such a small number we are going to follow up with tukeyhsd

```{r}
plot(TukeyHSD(model1))
```

The Middle-Back and Front-Back confidence intervals are less than zero than the results would be significantly different. 

## Conclusions


